---
title: "Simulation Study"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(pdc)
library(simts)
```

 
## Simulation 1 

We consider the linear model based on the vector

\[
\begin{aligned}
  \boldsymbol{\beta}^T &= [1,
    \underbrace{0, \ldots, 0}_\text{58} , 1], &\text{(Case 1)}\\
  \boldsymbol{\beta}^T &= [1,
    \underbrace{0, \ldots, 0}_\text{58} , 1, \underbrace{0, \ldots, 0}_\text{100}],  &\text{(Case 2)}
\end{aligned}
\]

and the following

- $\sigma^2 = 1$
- The covariates are standard normal realizations with pairwise correlation given by $corr(x_j, x_k) = 0.5^{|j-k|}$
- $n = 80$ and $n^\ast = 800$
- $B = 500$ (Monte-Carlo replications)

### Case 1: $n > p$

```{r simu1_case1, fig.align='center', cache = TRUE, fig.height=5, fig.width=6}
simu1_part1 <- run_simulation(nb_simu = 500, true_beta = c(1, rep(0,58), 1),
                              n = 80, n_star = 800, sigma = 1, cor_X = 0.5,
                              xlim = c(1.035, 1.09), ylim = c(2.35, 5.2),
                              xlab = expression(PE[y]), 
                              ylab = "Mean(#sel.)",
                              title = "Simulation 1: n > p",
                              adaptive = FALSE)  
kable(simu1_part1)  
```

### Case 2: $n < p$ 

```{r simu1_case2, fig.align='center', cache = TRUE, fig.height=5, fig.width=6}
simu1_part2 <- run_simulation(nb_simu = 500, true_beta = c(1, rep(0,58), 1, rep(0, 100)),
                              n = 80, n_star = 800, sigma = 1, cor_X = 0.5,
                              xlim = c(1.035, 1.225), ylim = c(2.5, 8.5),
                              xlab = expression(PE[y]), 
                              ylab = "Mean(#sel.)",
                              title = "Simulation 1: n < p",
                              adaptive = FALSE)  
kable(simu1_part2)  
```

## Simulation 2

We consider the linear model based on the vector

\[
\begin{aligned}
  \boldsymbol{\beta}^T &= [2, 0, 1, 2, 0, 1, \underbrace{0, \ldots, 0}_\text{16}, \underbrace{0.1, \ldots, 0.1}_\text{6}, \underbrace{0, \ldots, 0}_\text{16}, 2, 0, 1, 2, 0, 1], &\text{(Case 1)}\\
  \boldsymbol{\beta}^T &= [2, 0, 1, 2, 0, 1, \underbrace{0, \ldots, 0}_\text{16}, \underbrace{0.1, \ldots, 0.1}_\text{6}, \underbrace{0, \ldots, 0}_\text{16}, 2, 0, 1, 2, 0, 1, \underbrace{0, \ldots, 0}_\text{100}],  &\text{(Case 2)}
\end{aligned}
\]

and the following

- $\sigma^2 = 2$
- The covariates are standard normal realizations with pairwise correlation given by $corr(x_j, x_k) = 0.5^{|j-k|}$
- $n = 100$ and $n^\ast = 1000$
- $B = 500$ (Monte-Carlo replications)

### Case 1: $n > p$

```{r simu2_case1, fig.align='center', cache = TRUE, fig.height=5, fig.width=6}
beta <- c(rep(c(2, 0, 1), 2),rep(0, 16),rep(0.1, 6),rep(0, 16),rep(c(2, 0, 1), 2))
simu2_part1 <- run_simulation(nb_simu = 500, true_beta = beta,
                              n = 100, n_star = 1000, sigma = 2, cor_X = 0.5,
                              xlim = c(4.73, 5.4), ylim = c(7.5, 16),
                              xlab = expression(PE[y]),
                              ylab = "Mean(#sel.)", 
                              title = "Simulation 2: n > p",
                              adaptive = FALSE)  
kable(simu2_part1)  
```

### Case 2: $n < p$ 

```{r simu2_case2, fig.align='center', cache = TRUE, fig.height=5, fig.width=6}
beta <- c(rep(c(2, 0, 1), 2), rep(0, 16), rep(0.1, 6), rep(0, 16), rep(c(2, 0, 1), 2), rep(0, 100))
simu2_part2 <- run_simulation(nb_simu = 500, true_beta = beta,
                              n = 100, n_star = 1000, sigma = 2, cor_X = 0.5,
                              xlim = c(4.9, 5.8), ylim = c(7.5, 21),
                              xlab = expression(PE[y]),
                              ylab = "Mean(#sel.)", 
                              title = "Simulation 2: n < p",
                              adaptive = FALSE)  
kable(simu2_part2)  
```


## Simulation 3

We consider the linear model based on the vector

\[
\begin{aligned}
  \boldsymbol{\beta}^T &= [3, \underbrace{0, \ldots, 0}_\text{5}, 1, \underbrace{0, \ldots, 0}_\text{10}, 0.05, 0.05, 0.05, \underbrace{0, \ldots, 0}_\text{10}, 2, \underbrace{0, \ldots, 0}_\text{20}], &\text{(Case 1)}\\
  \boldsymbol{\beta}^T &= [3, \underbrace{0, \ldots, 0}_\text{5}, 1, \underbrace{0, \ldots, 0}_\text{10}, 0.05, 0.05, 0.05, \underbrace{0, \ldots, 0}_\text{10}, 2, \underbrace{0, \ldots, 0}_\text{120}],  &\text{(Case 2)}
\end{aligned}
\]

and the following

- $\sigma^2 = 3$
- The covariates are standard normal realizations with pairwise correlation given by $corr(x_j, x_k) = 0.25^{|j-k|}$
- $n = 100$ and $n^\ast = 1000$
- $B = 500$ (Monte-Carlo replications)
   
### Case 1: $n > p$ 
 
```{r simu3_case1, fig.align='center', cache = TRUE, fig.height=5, fig.width=6}
beta <- c(3,rep(0,5),1,rep(0,10),rep(0.05,3),rep(0,10),2,rep(0,20))
simu3_part1 <- run_simulation(nb_simu = 500, true_beta = beta,
                              n = 100, n_star = 1000, sigma = 3, cor_X = 0.25,
                              xlim = c(9.65, 10.5), ylim = c(3, 11.5),
                              xlab = expression(PE[y]), 
                              ylab = "Mean(#sel.)", 
                              title = "Simulation 3: n > p",
                              adaptive = FALSE)
kable(simu3_part1)  
```


### Case 2: $n < p$ 
 
```{r simu3_case2, fig.align='center', cache = TRUE, fig.height=5, fig.width=6}
beta <- c(3,rep(0,5),1,rep(0,10),rep(0.05,3),rep(0,10),2,rep(0,20))
simu3_part2 <- run_simulation(nb_simu = 500, true_beta = beta,
                              n = 100, n_star = 1000, sigma = 3, cor_X = 0.25,
                              xlim = c(9.65, 10.5), ylim = c(3, 12),
                              xlab = expression(PE[y]), 
                              ylab = "Mean(#sel.)", 
                              title = "Simulation 3: n < p",
                              adaptive = FALSE)
kable(simu3_part2)  
```


## Simulation 4
   
Same setting as Simulation 3 but the first column of $\mathbf{X}$ is unobserved.

### Case 1: $n > p$ 

```{r simu4_case1, fig.align='center', cache = TRUE, fig.height=5, fig.width=6}
beta <- c(3,rep(0,5),1,rep(0,10),rep(0.05,3),rep(0,10),2,rep(0,20))
simu4_part1 <- run_simulation(nb_simu = 500, true_beta = beta,
                              n = 100, n_star = 1000, sigma = 3, cor_X = 0.25,
                              xlim = c(19.3,20.2), ylim = c(1.5, 14),
                              xlab = expression(PE[y]), 
                              ylab = "Mean(#sel.)", 
                              title = "Simulation 4: n > p",
                              adaptive = FALSE, omitted_variables = 1)
kable(simu4_part1)  
```
 
### Case 2: $n < p$ 

```{r simu4_case2, fig.align='center', cache = TRUE, fig.height=5, fig.width=6}
beta <- c(3,rep(0,5),1,rep(0,10),rep(0.05,3),rep(0,10),2,rep(0,120))
simu4_part2 <- run_simulation(nb_simu = 500, true_beta = beta, 
                              n = 100, n_star = 1000, sigma = 3, cor_X = 0.25,
                              xlim = c(19.5,20.7), ylim = c(1.5, 20),
                              xlab = expression(PE[y]), 
                              ylab = "Mean(#sel.)", 
                              title = "Simulation 4: n < p",
                              adaptive = FALSE, omitted_variables = 1)
kable(simu4_part2)  
```

