---
title: "Simulation Study"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(pdc)
library(simts)
```

 
## Simulation 1 

We consider the linear model based on the vector

\[
\begin{aligned}
  \boldsymbol{\beta}^T &= [1,
    \underbrace{0, \ldots, 0}_\text{58} , 1], &\text{(Case 1)}\\
  \boldsymbol{\beta}^T &= [1,
    \underbrace{0, \ldots, 0}_\text{58} , 1, \underbrace{0, \ldots, 0}_\text{100}],  &\text{(Case 2)}
\end{aligned}
\]

and the following

- $\sigma^2 = 1$
- The covariates are standard normal realizations with pairwise correlation given by $corr(x_j, x_k) = 0.5^{|j-k|}$
- $n = 80$ and $n^\ast = 800$
- $B = 500$ (Monte-Carlo replications)

### Case 1: $n > p$

```{r simu1_case1, fig.align='center', cache = TRUE, fig.height=5, fig.width=6}
simu1_part1 <- run_simulation(nb_simu = 100, 
                              true_beta = c(1, rep(0,58), 1),
                              n = 80, n_star = 800, sigma = 1, 
                              cor_X = 0.5,
                              adaptive = FALSE)  
```

```{r simu1_case1_graph1, fig.align='center', fig.height=4.8, fig.width=10, dependson="simu1_case1"}
plot(simu1_part1, xlim = c(1,1.8), ylim = c(0.1,0.6), coef.correct = 1.1)
```

```{r simu1_case1_graph2, fig.align='center', fig.height=4.8, fig.width=5, dependson="simu1_case1"}
plot(simu1_part1, add_correct = FALSE, add_selected = FALSE)
```

```{r simu1_case1_table}
kable(simu1_part1$summary_table) 
```
